---
title: ''
output: html_document
---

```{r setup, include=FALSE}

## Loading Packages
library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)
library(acs)
library(stringr)

## Setting Formatting for output
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
## Formatting for Graphics
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)


#Read in files
county_pop<- readxl::read_xlsx("raw_data/county/county_pop.xlsx")
county_edu<- readxl::read_xlsx("raw_data/county/county_edu.xlsx")
county_insurance<- readxl::read_xlsx("raw_data/county/county_insurance.xlsx")
county_poverty<- readxl::read_xlsx("raw_data/county/county_poverty.xlsx")
county_nativity<- readxl::read_xlsx("raw_data/county/county_nativity.xlsx")
county_LEP<- readxl::read_xlsx("raw_data/county/county_LEP.xlsx")
county_cvap<- readxl::read_xlsx("raw_data/county/county_cvap_alone.xlsx")

## Using the lookup table to merge in Group Names and the proper population ID names
pop_id_lookup <- read_csv("raw_data/pop_id_lookup.csv") #Look-up table

county_pop <- county_pop %>% rename(pop_id = popgroupid)
county_pop<-county_pop %>% left_join(pop_id_lookup) %>% select( -pop_id)

county_edu <- county_edu %>% rename(pop_id = popgroupid)
county_edu<-county_edu %>% left_join(pop_id_lookup) %>% select( -pop_id)

county_insurance <- county_insurance %>% rename(pop_id = popgroupid)
county_insurance<-county_insurance %>% left_join(pop_id_lookup) %>% select( -pop_id)

county_poverty <- county_poverty %>% rename(pop_id = popgroupid)
county_poverty<-county_poverty %>% left_join(pop_id_lookup) %>% select( -pop_id)

county_nativity <- county_nativity %>% rename(pop_id = popgroupid)
county_nativity<-county_nativity %>% left_join(pop_id_lookup) %>% select( -pop_id)

county_LEP <- county_LEP %>% rename(pop_id = popgroupid)
county_LEP<-county_LEP %>% left_join(pop_id_lookup) %>% select( -pop_id)


### Specifying Groups
groups_alone <- c("Total population", "Asian alone", "NHPI alone")
groups_combo <- c("Total population", "Asian alone or combo", "NHPI alone or combo")
groups_race <- c("Total population", "Asian alone", "NHPI alone", "Asian alone or combo", "NHPI alone or combo")

groups_asian_detail_alone <-pop_id_lookup %>%
  filter(group_id == "Asian Detail") %>% 
  select(group_name) %>% pull()

groups_asian_detail_combo <-pop_id_lookup %>%
  filter(group_id == "Asian Detail Combo") %>% 
  select(group_name) %>%  pull()

groups_nhpi_detail_alone <-pop_id_lookup %>%
  filter(group_id == "NHPI Detail") %>% 
  select(group_name) %>%  pull()

groups_nhpi_detail_combo <-pop_id_lookup %>%
  filter(group_id == "NHPI Detail Combo") %>% 
  select(group_name) %>%  pull()
  
## Function that will take excel file and make it long
county_convert_long <- function(data){
  data %>%
  gather(estimate_type,
         estimate,
         -County,
         -Group,
         -group_id)
}


 county_display_table <- function(data, whichgroup, whichestimates){
   data %>%
     filter(Group %in% whichgroup) %>%
     filter(estimate_type %in% whichestimates) %>%
     select(-group_id) %>%
     mutate(long_key=paste(Group, estimate_type, sep=": ")) %>% #Combining Pop_ID and Estimate type
     select(-Group, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) %>% separate(County, into = c("County","State"), sep = ",") %>%
     arrange(State)%>%
     select(County,State,starts_with("Total population"),everything()) %>% 
      datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'Bfrt',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 2),
                lengthMenu = c(25, 50, 100), pageLength = 50))
 }


```



```{r setup pop, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
county_pop <- county_pop %>% 
   mutate(est_tot_pop = 
            case_when( check_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
         est_county_pop  =
          case_when( check_county_pop == 1 ~  NA_real_ ,TRUE ~ est_county_pop))

# Dropping those indicators
county_pop <- county_pop %>% select(-check_tot_pop,
                                  -check_county_pop,
                                  -geoid)



county_pop_map <- county_pop

# Renaming columns
county_pop<- county_pop %>% rename(Total = est_tot_pop,
         `Population` = est_county_pop,
         Group = group_name,
         `% of the Pop`= pct_pop,
         County = geodisplaylabel)



## Converting it to Long
county_pop_long <- county_convert_long(county_pop)

## Column Specification
pop_estimates <- c("Total")
pop_percent <- c("% of the Pop")

### Calculating Average for the sentence
avg_aa_pop <- county_pop %>% filter(Group == "Asian alone") %>% select(County, `% of the Pop`) %>%  summarize(mean = mean(`% of the Pop`, na.rm=TRUE)) %>% pull() %>% round(.,4)
avg_aa_pop <- avg_aa_pop*100
 
avg_pi_pop <- county_pop %>% filter(Group == "NHPI alone") %>% select(County, `% of the Pop`) %>%  summarize(mean = mean(`% of the Pop`, na.rm=TRUE)) %>% pull() %>% round(.,4)
avg_pi_pop <- avg_pi_pop*100

### For main topic sentence
aa_largest_countyname <- county_pop %>% filter(Group == "Asian alone") %>% top_n(1,`% of the Pop`) %>% pull(County)
aa_largest_county_pct <- county_pop %>% filter(Group == "Asian alone") %>% top_n(1,`% of the Pop`) %>% pull(`% of the Pop`)
aa_largest_county_pct <- round(aa_largest_county_pct*100,0)


```


```{r setup education, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
county_edu <- county_edu %>% 
  mutate(est_hsless = 
            case_when( check_hsless == 1 ~  NA_real_ ,TRUE ~ est_hsless),
         est_hs_ged  =
          case_when( check_hs_ged == 1 ~  NA_real_ ,TRUE ~ est_hs_ged),
         est_somecollegeaa  =
          case_when( check_some_college == 1 ~  NA_real_ ,TRUE ~ est_some_college),
         est_bahigher  =
          case_when( check_ba_higher == 1 ~  NA_real_ ,TRUE ~ est_ba_higher),
         est_tot_pop = 
           case_when(check_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop))
# Dropping those indicators
county_edu <- county_edu %>% select(-check_hsless,
                                  -check_hs_ged,
                                  -check_some_college,
                                  -check_ba_higher,
                                  -check_ba_higher,
                                  -check_tot_pop,
                                  -geoid)

# Create Columns
county_edu <- county_edu %>% mutate(
 pct_hsless   = est_hsless/est_tot_pop,
 pct_bahigher = est_bahigher/ est_tot_pop,
 pct_hs_ged = est_hs_ged / est_tot_pop,
 pct_some_college = est_some_college / est_tot_pop)

county_edu <- county_edu %>% select(geodisplaylabel,
                                    group_name,
                                    est_tot_pop,
                                    pct_hsless,
                                    pct_hs_ged,
                                    pct_some_college,
                                    pct_bahigher,
                                    group_id)
  

# Renaming columns
county_edu<- county_edu %>% rename(`Total 25yrs+ Old` = est_tot_pop,
         Group = group_name,
         `% Less than HS`= pct_hsless,
         `% BA or higher` = pct_bahigher,
         `% Some College or AA` = pct_some_college,
         `% HS or GED` = pct_hs_ged,
         County = geodisplaylabel)


## Converting it to Long
county_edu_long <- county_convert_long(county_edu)



## Column Specification
education_percent <- c("Total 25yrs+ Old", "% Less than HS", "% BA or higher", "% HS or GED", "% Some College or AA")



### Calculating Average for the sentence
avg_hs_less <- county_edu %>% filter(Group == "Total population") %>% select(County, `% Less than HS`) %>%  summarize(mean = mean(`% Less than HS`,na.rm = T)) %>% pull() %>% round(.,4)
avg_hs_less <- avg_hs_less*100
 
avg_ba_higher <- county_edu %>% filter(Group == "Total population") %>% select(County,  `% BA or higher`) %>%  summarize(mean = mean( `% BA or higher`,na.rm = T)) %>% pull() %>% round(.,4)
avg_ba_higher <- avg_ba_higher*100


```

```{r setup LEP, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
county_LEP <- county_LEP %>% 
  mutate(est_tot_pop = 
            case_when( check_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
    est_lep = 
            case_when( check_lep == 1 ~  NA_real_ ,TRUE ~ est_lep),
         est_other_lang  =
          case_when( check_other_lang == 1 ~  NA_real_ ,TRUE ~ est_other_lang))
        
# Dropping those indicators
county_LEP <- county_LEP %>% select(-check_tot_pop,
                                  -check_lep,
                                  -check_other_lang,
                                  -geoid)



county_LEP_map <- county_LEP

# Renaming columns
county_LEP<- county_LEP %>% rename(Total = est_tot_pop,
         `LEP` = est_lep,
         Group = group_name,
         `Speak other language` = est_other_lang,
         `% LEP`= pct_lep,
         County = geodisplaylabel)


## Converting it to Long
county_LEP_long <- county_convert_long(county_LEP)
## add all outcome data here (just replace county_edu with another data name)

## Column Specification
LEP_estimates <- c("Total", "LEP", "Speak Other Language")
LEP_percent <- c("% LEP")


### Calculating Average for the sentence
avg_lep <- county_LEP %>% filter(Group == "Total population") %>% select(County, `% LEP`) %>%  summarize(mean = mean(`% LEP`,na.rm = T)) %>% pull() %>% round(.,4)
avg_lep <- avg_lep*100

```



```{r setup nativity, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
county_nativity <- county_nativity %>% 
  mutate(est_tot_pop = 
            case_when( check_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
         est_foreign_born  =
          case_when( check_foreign_born == 1 ~  NA_real_ ,TRUE ~ est_foreign_born))


# Dropping those indicators
county_nativity <- county_nativity %>% select(-check_tot_pop,
                                  -check_foreign_born,
                                  -geoid)

# Create Columns
county_nativity <- county_nativity %>% mutate(
pct_foreign_born   = est_foreign_born / est_tot_pop)

county_nativity_map <- county_nativity

# Renaming columns
county_nativity<- county_nativity %>% rename(Total = est_tot_pop,
         `Foreign Born` = est_foreign_born,
         Group = group_name,
         `% Foreign Born`= pct_foreign_born,
         County = geodisplaylabel)



## Converting it to Long
county_nativity_long <- county_convert_long(county_nativity)
## add all outcome data here (just replace county_edu with another data name)


## Column Specification
nativity_estimates <- c("Total", "Foreign Born")
nativity_percent <- c("% Foreign Born")



### Calculating Average for the sentence
avg_foreign_born <- county_nativity %>% filter(Group == "Total population") %>% select(County, `% Foreign Born`) %>%  summarize(mean = mean(`% Foreign Born`, na.rm = T)) %>% pull() %>% round(.,4)
avg_foreign_born <- avg_foreign_born*100
 
```

```{r setup poverty, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
county_poverty <- county_poverty %>% 
  mutate(est_tot_pop = 
            case_when( check_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
         est_below_pov  =
          case_when( check_below_pov == 1 ~  NA_real_ ,TRUE ~ est_below_pov),
         est_above_pov  =
          case_when( check_above_pov == 1 ~  NA_real_ ,TRUE ~ est_above_pov))

# Dropping those indicators
county_poverty <- county_poverty %>% select(-check_tot_pop,
                                  -check_below_pov,
                                  -check_above_pov,
                                  -geoid)

# Create Columns
county_poverty <- county_poverty %>% mutate(
 pct_below_pov   = est_below_pov/est_tot_pop,
 pct_above_pov = est_above_pov/ est_tot_pop)


county_poverty_map <- county_poverty

# Renaming columns
county_poverty<- county_poverty %>% rename(Total = est_tot_pop,
         `Below Poverty` = est_below_pov,
         `Above Poverty` = est_above_pov,
         Group = group_name,
         `% Below Poverty`= pct_below_pov,
         `% Above Poverty` = pct_above_pov,
         County = geodisplaylabel)




## Converting it to Long
county_poverty_long <- county_convert_long(county_poverty)
## add all outcome data here (just replace county_poverty with another data name)


## Column Specification
poverty_estimates <- c("Total", "Below Poverty", "Above Poverty")
poverty_percent <- c("% Below Poverty", "% Above Poverty")



### Calculating Average for the sentence
avg_below_pov <- county_poverty %>% filter(Group == "Total population") %>% select(County, `% Below Poverty`) %>%  summarize(mean = mean(`% Below Poverty`, na.rm=T)) %>% pull() %>% round(.,4)
avg_below_pov <- avg_below_pov*100



```

```{r setup cvap-alone, include = FALSE}
### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
county_cvap <- county_cvap %>% 
  mutate(est_county_cvap = 
            case_when( check_county_cvap == 1 ~  NA_real_ ,TRUE ~ est_county_cvap),
            est_aapi_cvap = 
            case_when( check_aapi_cvap == 1 ~  NA_real_ ,TRUE ~ est_aapi_cvap),
         est_aapi_pop  =
          case_when( check_aapi_pop == 1 ~  NA_real_ ,TRUE ~ est_aapi_pop))

# Dropping those indicators
county_cvap <- county_cvap %>% select(-check_county_cvap,
                                  -check_aapi_pop,
                                  -check_aapi_cvap)

# Create Columns
county_cvap <- county_cvap %>% mutate(
 pct_county_cvap   = est_county_cvap /est_county_pop)

county_cvap_map <- county_cvap

# Renaming columns
county_cvap<- county_cvap %>% rename(`Total Population`= est_county_pop,
         `Total CVAP` = est_county_cvap,
         `AAPI Pop`= est_aapi_pop,
         `AAPI CVAP`= est_aapi_cvap,
         `% AAPI CVAP` = pct_aapi_cvap,
         `% AAPI Pop`= pct_aapi_pop,
         `% County CVAP`= pct_county_cvap,
         County = geoname)


### Calculating Average for the sentence
avg_county_cvap <- county_cvap %>% select(County, `% County CVAP`) %>%  summarize(mean = mean(`% County CVAP`, na.rm=TRUE)) %>% pull() %>% round(.,4)
avg_county_cvap <- avg_county_cvap*100

avg_aapi_cvap <- county_cvap %>% select(County, `% AAPI CVAP`) %>%  summarize(mean = mean(`% AAPI CVAP`, na.rm=TRUE)) %>% pull() %>% round(.,4)
avg_aapi_cvap <- avg_aapi_cvap*100

```




<div class="jumbotron">
  <div class="container">
  <h1>County Data</h1>
  <p> About `r aa_largest_county_pct`% of the population in `r aa_largest_countyname` is Asian American, the highest in the country.</p>
<div class="btn-group" role="group" aria-label="Basic example">
  <a href="county_data.html#resident-population" type="button" class="btn btn-primary">Resident Population</a>
  <a href="county_data.html#citizen-voting-age-population" type="button" class="btn btn-primary">Citizen Voting Age Population</a>
  <a href="county_data.html#education" type="button" class="btn btn-primary">Education</a>
  <a href="county_data.html#limited-english-proficiency" type="button" class="btn btn-primary">Limited English Proficiency</a>
  <a href="county_data.html#nativity" type="button" class="btn btn-primary">Nativity</a>
  <a href="county_data.html#poverty" type="button" class="btn btn-primary">Poverty</a>
</div>
</div>
</div>

# Resident Population {.tabset .tabset-fade .tabset-pills}

<a href="#top"><div style="text-align:center">Back to Top</a></div>


> Population data is complied using Table [B03001](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B03001) from the 2015 ACS 5-Year estimates.
Nationally, about **`r avg_aa_pop`**% of Americans is Asian, and **`r avg_pi_pop`**% of Americans is NHPI.

## Major Racial Groups


```{r pop-race, echo=FALSE, message=FALSE, warning=FALSE}

  
 county_display_table(county_pop_long, groups_race,pop_estimates) %>% 
  formatCurrency(columns = c(3:7),currency = "", interval = 3, mark = ",", digits=0) 


```


## Detailed Asian Alone 


```{r pop-aa_alone, echo=FALSE, message=FALSE, warning=FALSE}

  
county_pop %>%
    filter(group_id %in% "Asian Detail") %>%
    select(-group_id, - `% of the Pop`,-`Population`) %>%
    spread(Group,Total,fill = NA) %>% separate(County, into = c("County","State"), sep = ",") %>%
    datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% 
  formatCurrency(columns = c(3:23),currency = "", interval = 3, mark = ",", digits=0) 


```


## Detailed NHPI Alone

```{r pop-nhpi_alone, echo=FALSE, message=FALSE, warning=FALSE}

  
county_pop %>%
    filter(group_id %in% "NHPI Detail") %>%
    select(-group_id, - `% of the Pop`,-`Population`) %>%
    spread(Group,Total,fill = NA) %>% separate(County, into = c("County","State"), sep = ",") %>%
    datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% 
  formatCurrency(columns = c(3:11),currency = "", interval = 3, mark = ",", digits=0) 

```

## Detailed Asian Combo


```{r pop_aa_alone, echo=FALSE, message=FALSE, warning=FALSE}

  
county_pop %>%
    filter(group_id %in% "Asian Detail Combo") %>%
    select(-group_id, - `% of the Pop`,-`Population`) %>%
    spread(Group,Total,fill = NA) %>% separate(County, into = c("County","State"), sep = ",") %>%
    datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% 
  formatCurrency(columns = c(3:23),currency = "", interval = 3, mark = ",", digits=0) 


```


## Detailed NHPI Combo

```{r pop_nhpi_alone, echo=FALSE, message=FALSE, warning=FALSE}

  
county_pop %>%
    filter(group_id %in% "NHPI Detail Combo") %>%
    select(-group_id, - `% of the Pop`,-`Population`) %>%
    spread(Group,Total,fill = NA) %>% separate(County, into = c("County","State"), sep = ",") %>%
    datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% 
  formatCurrency(columns = c(3:11),currency = "", interval = 3, mark = ",", digits=0) 

```



# Citizen Voting Age Population {.tabset .tabset-fade .tabset-pills}
<a href="#top"><div style="text-align:center">Back to Top</a></div>

> CVAP data is complied using Table [B05003](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B05003) from the 2015 ACS 5-Year estimates.
Nationally, about **`r avg_county_cvap`**% of Americans are eligible to vote, while the national average number for AAPI is **`r avg_aapi_cvap`**%

## Raw Asian & NHPI Alone


```{r cvap-alone-raw, echo=FALSE, message=FALSE, warning=FALSE}

county_cvap_estimate <- county_cvap %>% select(County, `Total CVAP`, `AAPI CVAP`, `Total Population`, `AAPI Pop`) %>% separate(County, into = c("County","State"), sep = ",")

datatable(county_cvap_estimate, extensions = list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(3:6),currency = "", interval = 3, mark = ",", digits=0)
```

## % Asian & NHPI alone


```{r CVAP-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_cvap_pct <- county_cvap %>% select(County, `% AAPI CVAP`, `% AAPI Pop`) %>% separate(County, into = c("County","State"), sep = ",")

datatable(county_cvap_pct, extensions = list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatPercentage(columns = c(3:4), digits = 1)


```



# Education {.tabset .tabset-fade .tabset-pills}
<a href="#top"><div style="text-align:center">Back to Top</a></div>

> Educational Attainment data is complied using Table [B15002](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B15002) from the 2015 ACS 5-Year estimates.
Nationally, about **`r avg_hs_less`**% of Americans have less than a High School diploma and about **`r avg_ba_higher`**% have a Bachelor's Degree or higher.

## % Asian & NHPI Alone


```{r EDU-alone-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_display_table(county_edu_long, groups_alone,education_percent) %>% formatPercentage(columns = c(3,4,5,6,8,9,10,11), digits = 1) %>% formatCurrency(columns = c(7,12),currency = "", interval = 3, mark = ",", digits=0)


```

## % Asian & NHPI Combo


```{r EDU-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_display_table(county_edu_long, groups_combo,education_percent) %>% formatPercentage(columns = c(3:6, 8:11, 13:16), digits = 1) %>% formatCurrency(columns = c(7,12,17),currency = "", interval = 3, mark = ",", digits=0)

```



# Limited English Proficiency {.tabset .tabset-fade .tabset-pills}
<a href="#top"><div style="text-align:center">Back to Top</a></div>

> Limited English Proficiency (LEP) refers to the proportion of individuals who speak a language other than english at home & speak english less than "very well".
Limited English Proficiency data is complied using Table [B16004](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B16004) from the 2015 ACS 5-Year estimates.
Nationally Among Americans who speak a language other than english at home, about **`r avg_lep`**% of them speak English less than "very well".

## % Asian & NHPI Alone

```{r LEP-alone-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_display_table(county_LEP_long, groups_alone,LEP_percent) %>% formatPercentage(columns = c(3:5), digits = 1)


```

## % Asian & NHPI Combo


```{r LEP-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_display_table(county_LEP_long, groups_combo,LEP_percent) %>% formatPercentage(columns = c(3:5), digits = 1)


```

## Raw Asian & NHPI Alone


```{r LEP-combo-Alone, echo=FALSE, message=FALSE, warning=FALSE}

  
 county_display_table(county_LEP_long, groups_alone,LEP_estimates) %>% 
  formatCurrency(columns = c(3:8),currency = "", interval = 3, mark = ",", digits=0) 


```


## Raw Asian & NHPI Combo

```{r LEP-Combo, echo=FALSE, message=FALSE, warning=FALSE}

 county_display_table(county_LEP_long, groups_combo,LEP_estimates) %>% 
  formatCurrency(columns = c(3:8),currency = "", interval = 3, mark = ",", digits=0) 



```

# Nativity {.tabset .tabset-fade .tabset-pills}
<a href="#top"><div style="text-align:center">Back to Top</a></div>

> Nativity data is complied using Table [B05012](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B05012) from the 2015 ACS 5-Year estimates.
Nationally, about **`r avg_foreign_born`**% of Americans are foreign born.

## % Asian & NHPI Alone


```{r nativity-alone-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_display_table(county_nativity_long, groups_alone,nativity_percent) %>% formatPercentage(columns = c(3:5), digits = 1)


```

## % Asian & NHPI Combo



```{r nativity-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_display_table(county_nativity_long, groups_combo,nativity_percent) %>% formatPercentage(columns = c(3:5), digits = 1)


```

## Raw Asian & NHPI Alone


```{r nativity-combo-Alone, echo=FALSE, message=FALSE, warning=FALSE}

  
 county_display_table(county_nativity_long, groups_alone,nativity_estimates) %>% 
  formatCurrency(columns = c(3:8),currency = "", interval = 3, mark = ",", digits=0) 


```


## Raw Asian & NHPI Combo

```{r nativity-Combo, echo=FALSE, message=FALSE, warning=FALSE}

 county_display_table(county_nativity_long, groups_combo,nativity_estimates) %>% 
  formatCurrency(columns = c(3:8),currency = "", interval = 3, mark = ",", digits=0) 



```

# Poverty {.tabset .tabset-fade .tabset-pills}
<a href="#top"><div style="text-align:center">Back to Top</a></div>

> Poverty data is complied using Table [B17001](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B17001) from the 2015 ACS 5-Year estimates.
Nationally, about **`r avg_below_pov`**% of Americans are living below poverty line.

## % Asian & NHPI Alone


```{r poverty-alone-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_display_table(county_poverty_long, groups_alone,poverty_percent) %>% formatPercentage(columns = c(3:5), digits = 1)

```

## % Asian & NHPI Combo


```{r poverty-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

county_display_table(county_poverty_long, groups_combo,poverty_percent) %>% formatPercentage(columns = c(3:5), digits = 1)


```

## Raw Asian & NHPI Alone


```{r poverty-combo-Alone, echo=FALSE, message=FALSE, warning=FALSE}

  
 county_display_table(county_poverty_long, groups_alone,poverty_estimates) %>% 
  formatCurrency(columns = c(3:8),currency = "", interval = 3, mark = ",", digits=0) 


```


## Raw Asian & NHPI Combo

```{r poverty-Combo, echo=FALSE, message=FALSE, warning=FALSE}

 county_display_table(county_poverty_long, groups_combo,poverty_estimates) %>% 
  formatCurrency(columns = c(3:8),currency = "", interval = 3, mark = ",", digits=0) 



```

