---
title: ''
output: html_document
---

```{r setup, include=FALSE}

## Loading Packages
library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)
library(acs)
library(stringr)

## Setting Formatting for output
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
## Formatting for Graphics
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)


#Read in files
district_pop <- readxl::read_xlsx("raw_data/district/congressional_pop.xlsx")
district_pop <- district_pop %>% mutate(geodisplaylabel = 
                                str_replace(string = geodisplaylabel, pattern = "\\(115th Congress\\)", replacement = ""))
district_pop <- district_pop %>% separate(geodisplaylabel, into = c("District", "State"), sep = ",")

district_origin_aa <- readxl::read_xlsx("raw_data/district/congressional_detailed_aa.xlsx")
district_origin_aa <- district_origin_aa %>% mutate(geodisplaylabel = 
                                str_replace(string = geodisplaylabel, pattern = "\\(115th Congress\\)", replacement = ""))
district_origin_aa <- district_origin_aa %>% separate(geodisplaylabel, into = c("District", "State"), sep = ",")

district_origin_nhpi <- readxl::read_xlsx("raw_data/district/congressional_detailed_nhpi.xlsx")
district_origin_nhpi <- district_origin_nhpi %>% mutate(geodisplaylabel = 
                                str_replace(string = geodisplaylabel, pattern = "\\(115th Congress\\)", replacement = ""))
district_origin_nhpi <- district_origin_nhpi %>% separate(geodisplaylabel, into = c("District", "State"), sep = ",")

district_edu <- readxl::read_xlsx("raw_data/district/congressional_edu.xlsx")
district_edu <- district_edu %>% mutate(Geography = 
                                str_replace(string = Geography, pattern = "\\(115th Congress\\)", replacement = ""))
district_edu <- district_edu %>% separate(Geography, into = c("District", "State"), sep = ",")

district_lep <- readxl::read_xlsx("raw_data/district/congressional_edu.xlsx")
district_edu <- district_edu %>% mutate(Geography = 
                                str_replace(string = Geography, pattern = "\\(115th Congress\\)", replacement = ""))
district_edu <- district_edu %>% separate(Geography, into = c("District", "State"), sep = ",")




### Renaming Pop
district_pop <- district_pop %>% rename(
  `Total Population`= est_tot_pop,
  `Asian Alone` = est_aa_alone,
  `Asian Alone % Total Pop` = pct_aa_alone,
  `Asian Combo` = est_aa_combo,
  `Asian Combo % Total Pop` = pct_aa_combo,
  `NHPI Alone` = est_nhpi_alone,
  `NHPI Alone % Total Pop` = pct_nhpi_alone,
  `NHPI Combo` = est_nhpi_combo,
  `NHPI Combo % Total pop` = pct_nhpi_combo
)

district_rawnumbers <- c("District","State", "Total Population", "Asian Alone", "Asian Combo", "NHPI Alone", "NHPI Combo")
district_percent <- c("District","State", "Total Population", "Asian Alone % Total Pop", "Asian Combo % Total Pop", "NHPI Alone % Total Pop", "NHPI Combo % Total pop")

 district_display_table <- function(data, whichestimates){
   data %>%
    select(whichestimates) %>%
     arrange(State)%>%
     select(District, State,starts_with("Total population"),everything()) %>% 
      datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 1),
                lengthMenu = c(25, 50, 100), pageLength = 50))
 }
 

 ## Sentence for geo-highlight
largest_district_aa <- district_pop %>% top_n(1,`Asian Alone % Total Pop`) %>% pull(District)
largest_district_aa_state <- district_pop %>% top_n(1,`Asian Alone % Total Pop`) %>% pull(State)
largest_district_aa_pct <- district_pop %>% top_n(1,`Asian Alone % Total Pop`) %>% pull(`Asian Alone % Total Pop`)

largest_district_aa_pct<- round(largest_district_aa_pct*100,0)
```

```{r setup-detailed origin, include=FALSE}


district_aa_origin_counts <- district_origin_aa %>% select(District, State, starts_with("Hd01_"))
district_aa_origin_pct <- district_origin_aa %>% select(District, State,hd01_vd01, starts_with("pct_"))

district_nhpi_origin_counts <- district_origin_nhpi %>% select(District, State, starts_with("Hd01_"))
district_nhpi_origin_pct <- district_origin_nhpi %>% select(District, State,hd01_vd01, starts_with("pct_"))


district_aa_origin_counts <- district_aa_origin_counts %>% rename(
"Total Asian Alone" = hd01_vd01,
"Asian Indian" = hd01_vd02,
"Bangladeshi" = hd01_vd03,
"Bhutanese" = hd01_vd04,
"Burmese" = hd01_vd05,
"Cambodian" = hd01_vd06,
"Chinese" = hd01_vd07,
"Filipino" = hd01_vd08,
"Hmong" = hd01_vd09,
"Indonesian" = hd01_vd10,
"Japanese" = hd01_vd11,
"Korean" = hd01_vd12,
"Laotian" = hd01_vd13,
"Malaysian" = hd01_vd14,
"Mongolian" = hd01_vd15,
"Nepalese" = hd01_vd16,
"Okinawan" = hd01_vd17,
"Pakistani" = hd01_vd18,
"Sri Lankan" = hd01_vd19,
"Taiwanese" = hd01_vd20,
"Thai" = hd01_vd21,
"Vietnamese" = hd01_vd22,
"Other Asian, specified" = hd01_vd23,
"Other Asian, not specified" = hd01_vd24,
"Two or more Asian" = hd01_vd25)

district_aa_origin_pct <- district_aa_origin_pct %>% rename(
  "Total Asian Alone" = hd01_vd01,
"Asian Indian" = pct_hd01_vd02,
"Bangladeshi" = pct_hd01_vd03,
"Bhutanese" = pct_hd01_vd04,
"Burmese" = pct_hd01_vd05,
"Cambodian" = pct_hd01_vd06,
"Chinese, except Taiwanese" = pct_hd01_vd07,
"Filipino" = pct_hd01_vd08,
"Hmong" = pct_hd01_vd09,
"Indonesian" = pct_hd01_vd10,
"Japanese" = pct_hd01_vd11,
"Korean" = pct_hd01_vd12,
"Laotian" = pct_hd01_vd13,
"Malaysian" = pct_hd01_vd14,
"Mongolian" = pct_hd01_vd15,
"Nepalese" = pct_hd01_vd16,
"Okinawan" = pct_hd01_vd17,
"Pakistani" = pct_hd01_vd18,
"Sri Lankan" = pct_hd01_vd19,
"Taiwanese" = pct_hd01_vd20,
"Thai" = pct_hd01_vd21,
"Vietnamese" = pct_hd01_vd22,
"Other Asian, specified" = pct_hd01_vd23,
"Other Asian, not specified" = pct_hd01_vd24,
"Two or more Asian" = pct_hd01_vd25)

district_nhpi_origin_counts <- district_nhpi_origin_counts %>% rename(
"Total NHPI Alone" = hd01_vd01, 
"Native Hawaiian" = hd01_vd03, 
"Samoan" = hd01_vd04, 
"Tongan" = hd01_vd05, 
"Other Polynesian" = hd01_vd06, 
"Guamanian or Chamorro" = hd01_vd08, 
"Marshallese" = hd01_vd09, 
"Other Micronesian" = hd01_vd10, 
"Fijian" = hd01_vd12, 
"Other Melanesian" = hd01_vd13, 
"Other Pacific Islander" = hd01_vd14, 
"Two or More NHPI" = hd01_vd15 
)

district_nhpi_origin_pct<- district_nhpi_origin_pct %>% rename(
"Total NHPI Alone" = hd01_vd01, 
"Native Hawaiian" = pct_hd01_vd03, 
"Samoan" = pct_hd01_vd04, 
"Tongan" = pct_hd01_vd05, 
"Other Polynesian" = pct_hd01_vd06, 
"Guamanian or Chamorro" = pct_hd01_vd08, 
"Marshallese" = pct_hd01_vd09, 
"Other Micronesian" = pct_hd01_vd10, 
"Fijian" = pct_hd01_vd12, 
"Other Melanesian" = pct_hd01_vd13, 
"Other Pacific Islander" = pct_hd01_vd14, 
"Two or More NHPI" = pct_hd01_vd15 
)


```

```{r setup-education, include=FALSE}

### Renaming Education
district_edu <- district_edu %>% rename(
"Total Asian alone" = est_aa_alone,
"AA less than HS" = est_aa_hsless,
"% AA less than HS" = pct_aa_hsless,
"AA HS Diploma or GED" = est_aa_hs_ged,
"% AA HS Diploma or GED" = pct_aa_hs_ged,
"AA Some College" = est_aa_some_college,
"% AA Some College" = pct_aa_some_college,
"AA BA or higher" = est_aa_ba_higher,
"% AA BA or higher" = pct_aa_ba_higher,
"Total NHPI alone" = est_nhpi_alone,
"NHPI less than HS" = est_nhpi_hsless,
"% NHPI less than HS" = pct_nhpi_hsless,
"NHPI HS Diploma or GED" = est_nhpi_hs_ged,
"% NHPI HS Diploma or GED" = pct_nhpi_hs_ged,
"NHPI Some College" = est_nhpi_some_college,
"% NHPI Some College" = pct_nhpi_some_collge,
"NHPI BA or higher" = est_nhpi_ba_higher,
"% NHPI BA or higher" = pct_nhpi_ba_higher
)

district_edu_count <- district_edu %>% select(District, State, `Total Asian alone`, starts_with("AA"), `Total NHPI alone`, starts_with("NHPI")) %>% colnames()
district_edu_percent <- district_edu %>% select(District, State, `Total Asian alone`, starts_with("% AA"), `Total NHPI alone`, starts_with("% NHPI")) %>% colnames()


```

<div class="jumbotron">
  <div class="container">
  <h1>Congressional District Data</h1>
  <p> About `r largest_district_aa_pct`% of the population in `r largest_district_aa`, `r largest_district_aa_state` is Asian American, the highest in the country.</p>
<div class="btn-group" role="group" aria-label="Basic example">
  <a href="district_data.html#percent-aapi-population" type="button" class="btn btn-primary">AAPI Population</a>
  <a href="district_data.html#asian-american-detailed-origin" type="button" class="btn btn-primary">Asian Origin</a>
  <a href="district_data.html#nhpi-american-detailed-origin" type="button" class="btn btn-primary">NHPI Origin</a>
  <a href="district_data.html#educational-attainment" type="button" class="btn btn-primary">Education</a>
</div>
</div>
</div>

# Population {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> Population data is complied using Tables: [B02001](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02001), [B02011](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02011), and [B02012](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02012) from the 2016 ACS 5-Year estimates.

  


## Percent AAPI Population 


```{r pop-pct, echo=FALSE, message=FALSE, warning=FALSE}

  
 district_display_table(district_pop,district_percent) %>% 
  formatCurrency(columns = c(3),currency = "", interval = 3, mark = ",", digits=0) %>%
  formatPercentage(columns = c(4,5,6,7),digits = 2)


```


## AAPI Population


```{r pop-number, echo=FALSE, message=FALSE, warning=FALSE}

  
 district_display_table(district_pop,district_rawnumbers) %>% 
  formatCurrency(columns = c(3:7),currency = "", interval = 3, mark = ",", digits=0)


```


# Asian American Detailed Origin {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> Population data is complied using Tables: [B02015](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02015) from the 2016 ACS 5-Year estimates.

## Percent Asian Detailed Origin

```{r pop-aa_origin-pct, echo=FALSE, message=FALSE, warning=FALSE}

  
 district_display_table(district_aa_origin_pct,colnames(district_aa_origin_pct)) %>% 
  formatCurrency(columns = c(3),currency = "", interval = 3, mark = ",", digits=0) %>%
  formatPercentage(columns = c(4:27),digits = 1)

```

## Asian Detailed Origin

```{r pop-aa_origin-count, echo=FALSE, message=FALSE, warning=FALSE}

 district_display_table(district_aa_origin_counts,colnames(district_aa_origin_counts)) %>% 
  formatCurrency(columns = c(3:27),currency = "", interval = 3, mark = ",", digits=0)

```





# NHPI American Detailed Origin {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> Population data is complied using Tables: [B02016](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02016) from the 2016 ACS 5-Year estimates.

## Percent NHPI Detailed Origin

```{r pop-nhpi-origin-pct, echo=FALSE, message=FALSE, warning=FALSE}

  
 district_display_table(district_nhpi_origin_pct,colnames(district_nhpi_origin_pct)) %>% 
  formatCurrency(columns = c(3),currency = "", interval = 3, mark = ",", digits=0) %>%
  formatPercentage(columns = c(4:14),digits = 1)

```

## Asian NHPI Origin

```{r pop-nhpi-origin-count, echo=FALSE, message=FALSE, warning=FALSE}

  
 district_display_table(district_nhpi_origin_counts,colnames(district_nhpi_origin_counts)) %>% 
  formatCurrency(columns = c(3:14),currency = "", interval = 3, mark = ",", digits=0)

```





# Educational Attainment {.tabset .tabset-fade .tabset-pills}


<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> Population data is complied using Tables: [B15002](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B15002) from the 2016 ACS 5-Year estimates.

## Percent AAPI Educational Attainment

```{r pop-edu-pct, echo=FALSE, message=FALSE, warning=FALSE}

 district_display_table(district_edu,district_edu_percent) %>% 
  formatCurrency(columns = c(3,8 ),currency = "", interval = 3, mark = ",", digits=0) %>%
  formatPercentage(columns= c(4,5,6,7,9,10,11,12), digits = 1)

```


## AAPI Educational Attainment

```{r pop-edu-count, echo=FALSE, message=FALSE, warning=FALSE}

 district_display_table(district_edu,district_edu_percent) %>% 
  formatCurrency(columns = c(3,8 ),currency = "", interval = 3, mark = ",", digits=0) %>%
  formatPercentage(columns= c(4,5,6,7,9,10,11,12), digits = 1)

```