---
title: ""
output: 
  html_document:
    md_extensions: +raw_html
    css: style.css
---

```{r setup, include=FALSE}

## Loading Packages
library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)
library(acs)
library(stringr)

## Setting Formatting for output
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
## Formatting for Graphics
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)


#Read in files
state_edu<- readxl::read_xlsx("raw_data/state/state_edu.xlsx")
state_LEP<- readxl::read_xlsx("raw_data/state/state_LEP.xlsx")
state_nativity<- readxl::read_xlsx("raw_data/state/state_nativity.xlsx")
state_poverty<- readxl::read_xlsx("raw_data/state/state_poverty.xlsx")
state_pop<- readxl::read_xlsx("raw_data/state/state_pop.xlsx")
state_cvap<- readxl::read_xlsx("raw_data/state/state_cvap_alone.xlsx")
## [rename the variable to pop_id] state_edu <- state_edu %>% rename(pop_id = popgroupid)

## Using the lookup table to merge in Group Names and the proper population ID names
pop_id_lookup <- read_csv("raw_data/pop_id_lookup.csv") #Look-up table
state_edu<-state_edu %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
state_LEP<-state_LEP %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
state_nativity<-state_nativity %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
state_poverty<-state_poverty %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
state_pop<-state_pop %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
### Specifying Groups
groups_alone <- c("Total population", "Asian alone", "NHPI alone")
groups_combo <- c("Total population", "Asian alone or combo", "NHPI alone or combo")
groups_race <- c("Total population", "Asian alone", "NHPI alone", "Asian alone or combo", "NHPI alone or combo")

groups_asian_detail_alone <-pop_id_lookup %>%
  filter(group_id == "Asian Detail") %>% 
  select(group_name) %>% pull()

groups_asian_detail_combo <-pop_id_lookup %>%
  filter(group_id == "Asian Detail Combo") %>% 
  select(group_name) %>%  pull()

groups_nhpi_detail_alone <-pop_id_lookup %>%
  filter(group_id == "NHPI Detail") %>% 
  select(group_name) %>%  pull()

groups_nhpi_detail_combo <-pop_id_lookup %>%
  filter(group_id == "NHPI Detail Combo") %>% 
  select(group_name) %>%  pull()
  

## Function that will take excel file and make it long
state_convert_long <- function(data){
  data %>%
  gather(estimate_type,
         estimate,
         -State,
         -Group,
         -group_id)
}


 state_display_table <- function(data, whichgroup, whichestimates){
   data %>%
     filter(Group %in% whichgroup) %>%
     filter(estimate_type %in% whichestimates) %>%
     select(-group_id) %>%
     mutate(long_key=paste(Group, estimate_type, sep=": ")) %>% #Combining Pop_ID and Estimate type
     select(-Group, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) %>%
     select(State,starts_with("Total population"),everything()) %>% 
      datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'Brt',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 1),
                lengthMenu = c(25, 50, 100), pageLength = 50))
 }


```


```{r setup poverty, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
state_poverty <- state_poverty %>% 
  mutate(est_tot_pop = 
            case_when( checking_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
         est_below_pov  =
          case_when( checking_below_pov == 1 ~  NA_real_ ,TRUE ~ est_below_pov),
         est_above_pov  =
          case_when( checking_above_pov == 1 ~  NA_real_ ,TRUE ~ est_above_pov))

# Dropping those indicators
state_poverty <- state_poverty %>% select(-checking_tot_pop,
                                  -checking_below_pov,
                                  -checking_above_pov)

# Create Columns
state_poverty <- state_poverty %>% mutate(
 pct_below_pov   = est_below_pov/est_tot_pop,
 pct_above_pov = est_above_pov/ est_tot_pop)


state_poverty_map <- state_poverty

# Renaming columns
state_poverty<- state_poverty %>% rename(Total = est_tot_pop,
         `Below Poverty` = est_below_pov,
         `Above Poverty` = est_above_pov,
         Group = group_name,
         `% Below Poverty`= pct_below_pov,
         `% Above Poverty` = pct_above_pov,
         State = geodisplaylabel)




## Converting it to Long
state_poverty_long <- state_convert_long(state_poverty)
## add all outcome data here (just replace state_poverty with another data name)


## Column Specification
poverty_estimates <- c("Total", "Below Poverty", "Above Poverty")
poverty_percent <- c("% Below Poverty", "% Above Poverty")



### Calculating Average for the sentence
avg_below_pov <- state_poverty %>% filter(Group == "Total population") %>% select(State, `% Below Poverty`) %>%  summarize(mean = mean(`% Below Poverty`, na.rm=T)) %>% pull() %>% round(.,4)
avg_below_pov <- avg_below_pov*100



```

<div class="jumbotron">
  <h1>Welcome to QuickStats</h1>
  <p>Here, you will find data on Asian Americans and Native Hawaiians/Other Pacific Islanders (NHPIs) in a format that is easy to sort, print, or download.</p>
   <p>Using the buttons below, select the level of geography.</p>
</div>



<div class="container">
  <div class="col-md-4 col-lg-6 text-center">
  <a href="national_data.html" type="button" class="btn btn-default btn-block">National</a>
  <a href="state_data.html" type="button" class="btn btn-default btn-block">State</a>
  <a href="county_data.html" type="button" class="btn btn-default btn-block">County</a>
  <a href="district_data.html" type="button" class="btn btn-default btn-block">Congressional District</a>
  <a href="metro_data.html" type="button" class="btn btn-default btn-block">Metropolitan Statistical Area</a>
  </div>
</div>


# Poverty {.tabset .tabset-fade .tabset-pills}

> Poverty data is complied using Table [B17001](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B17001) from the 2015 ACS 5-Year estimates.
Nationally, about **`r avg_below_pov`**% of Americans are living below poverty line.

## Map Asian Americans

> Greyed out states indicate that the ACS sample is not large enough to provide reliable estimates.


```{r poverty visualize-aa, echo=FALSE, message=FALSE, warning=FALSE}


 state_poverty_map <- state_poverty_map %>%
  gather(estimate_type,
         estimate,
         -geodisplaylabel,
         -group_name,
         -group_id)



 state_poverty_map <- state_poverty_map %>%
     filter(group_name %in% groups_combo) %>%
     filter(str_detect(estimate_type, "pct_")) %>%
     select(-group_id) %>%
     mutate(long_key=paste(group_name, estimate_type, sep="_")) %>% #Combining Pop_ID and Estimate type
     select(-group_name, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) 
  

state_poverty_map <- state_poverty_map %>% mutate(
  pct_state_below_pov = round(`Total population_pct_below_pov`*100,2),
  pct_asian_below_pov = round(`Asian alone or combo_pct_below_pov`*100,2),
  pct_nhpi_below_pov = round(`NHPI alone or combo_pct_below_pov`*100,2)
)



data(usgeojson)
highchart() %>%
  hc_title(text = "AAPI Data: Poverty", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_chart(backgroundColor = "#f0f0f0") %>%
  hc_add_series_map(usgeojson, state_poverty_map, name = "Below Poverty",value = "pct_asian_below_pov", joinBy = c("name", "geodisplaylabel"),
                    borderColor= "transparent",nullColor = "#bfbfbf") %>%
  hc_tooltip(useHTML=T,pointFormat = "In {point.name}, about <span style = 'color:#E26069'>{point.value:.0f}%</span> of Asian Americans live below the poverty line <br> compared to the state average of <span style = 'color:#E26069'>{point.pct_state_below_pov:.0f}%</span>.") %>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops= color_stops(n=9, colors =c("#ffffcc","#ffeda0", "#fed976","#feb24c", "#fd8d3c","#fc4e2a","#e31a1c", "#bd0026", "#800026")),labels= list(format = "{value}%"),showInLegend=T) %>%
  hc_legend(title = list(text= "Asian % Below Poverty by State", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) %>% 
  #hc_legend(layout = "vertical", align = "right",
   #         floating = TRUE, valueDecimals = 0, valueSuffix = "%") 
  hc_exporting(enabled = TRUE)

```




## Map Native Hawaiian & Pacific Islanders

> Greyed out states indicate that the ACS sample is not large enough to provide reliable estimates.


```{r poverty visualize-nhpi, echo=FALSE, message=FALSE, warning=FALSE}

highchart() %>%
  hc_title(text = "AAPI Data: Poverty", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_chart(backgroundColor = "#f0f0f0") %>%
  hc_add_series_map(usgeojson, state_poverty_map, name = "Below Poverty",value = "pct_nhpi_below_pov", joinBy = c("name", "geodisplaylabel"),
                    borderColor= "transparent",nullColor = "#bfbfbf") %>%
  hc_tooltip(useHTML=T,pointFormat = "In {point.name}, about <span style = 'color:#E26069'>{point.value:.0f}%</span> of NHPIs live below the poverty line <br> compared to the state average of <span style = 'color:#E26069'>{point.pct_state_below_pov:.0f}%</span>.") %>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops= color_stops(n=9, colors =c("#ffffcc","#ffeda0", "#fed976","#feb24c", "#fd8d3c","#fc4e2a","#e31a1c", "#bd0026", "#800026")),labels= list(format = "{value}%"),showInLegend=T) %>%
  hc_legend(title = list(text= "Asian % Below Poverty by State", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) %>% 
  #hc_legend(layout = "vertical", align = "right",
   #         floating = TRUE, valueDecimals = 0, valueSuffix = "%") 
  hc_exporting(enabled = TRUE)

```


