---
title: ''
output: html_document
---

```{r setup, include=FALSE}

## Loading Packages
library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)
library(acs)
library(stringr)

## Setting Formatting for output
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
## Formatting for Graphics
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)


#Read in files

msa_pop <- readxl::read_xlsx("raw_data/metro/msa_aapi_prop.xlsx")
msa_aa_origin <- readxl::read_xlsx("raw_data/metro/msa_detailed_aa.xlsx")
msa_nhpi_origin <- readxl::read_xlsx("raw_data/metro/msa_detailed_nhpi.xlsx")

msa_pop <- msa_pop %>% mutate(geodisplaylabel = 
                                str_replace(string = geodisplaylabel, pattern = "Metro Area", replacement = ""))
msa_aa_origin <- msa_aa_origin %>% mutate(geodisplaylabel = 
                                str_replace(string = geodisplaylabel, pattern = "Metro Area", replacement = ""))

msa_nhpi_origin <- msa_nhpi_origin %>% mutate(geodisplaylabel = 
                                str_replace(string = geodisplaylabel, pattern = "Metro Area", replacement = ""))

msa_aa_origin_counts <- msa_aa_origin %>% select(geodisplaylabel, starts_with("Hd01_"))
msa_aa_origin_pct <- msa_aa_origin %>% select(geodisplaylabel,hd01_vd01, starts_with("pct_"))

msa_nhpi_origin_counts <- msa_nhpi_origin %>% select(geodisplaylabel, starts_with("Hd01_"))
msa_nhpi_origin_pct <- msa_nhpi_origin %>% select(geodisplaylabel,hd01_vd01, starts_with("pct_"))


msa_aa_origin_counts <- msa_aa_origin_counts %>% rename(
"MSA" = geodisplaylabel,
"Total Asian Alone" = hd01_vd01,
"Asian Indian" = hd01_vd02,
"Bangladeshi" = hd01_vd03,
"Bhutanese" = hd01_vd04,
"Burmese" = hd01_vd05,
"Cambodian" = hd01_vd06,
"Chinese" = hd01_vd07,
"Filipino" = hd01_vd08,
"Hmong" = hd01_vd09,
"Indonesian" = hd01_vd10,
"Japanese" = hd01_vd11,
"Korean" = hd01_vd12,
"Laotian" = hd01_vd13,
"Malaysian" = hd01_vd14,
"Mongolian" = hd01_vd15,
"Nepalese" = hd01_vd16,
"Okinawan" = hd01_vd17,
"Pakistani" = hd01_vd18,
"Sri Lankan" = hd01_vd19,
"Taiwanese" = hd01_vd20,
"Thai" = hd01_vd21,
"Vietnamese" = hd01_vd22,
"Other Asian, specified" = hd01_vd23,
"Other Asian, not specified" = hd01_vd24,
"Two or more Asian" = hd01_vd25)

msa_aa_origin_pct <- msa_aa_origin_pct %>% rename(
  "MSA" = geodisplaylabel,
  "Total Asian Alone" = hd01_vd01,
"Asian Indian" = pct_hd01_vd02,
"Bangladeshi" = pct_hd01_vd03,
"Bhutanese" = pct_hd01_vd04,
"Burmese" = pct_hd01_vd05,
"Cambodian" = pct_hd01_vd06,
"Chinese" = pct_hd01_vd07,
"Filipino" = pct_hd01_vd08,
"Hmong" = pct_hd01_vd09,
"Indonesian" = pct_hd01_vd10,
"Japanese" = pct_hd01_vd11,
"Korean" = pct_hd01_vd12,
"Laotian" = pct_hd01_vd13,
"Malaysian" = pct_hd01_vd14,
"Mongolian" = pct_hd01_vd15,
"Nepalese" = pct_hd01_vd16,
"Okinawan" = pct_hd01_vd17,
"Pakistani" = pct_hd01_vd18,
"Sri Lankan" = pct_hd01_vd19,
"Taiwanese" = pct_hd01_vd20,
"Thai" = pct_hd01_vd21,
"Vietnamese" = pct_hd01_vd22,
"Other Asian, specified" = pct_hd01_vd23,
"Other Asian, not specified" = pct_hd01_vd24,
"Two or more Asian" = pct_hd01_vd25)

msa_nhpi_origin_counts <- msa_nhpi_origin_counts %>% rename(
"MSA"= geodisplaylabel,
"Total NHPI Alone" = hd01_vd01,
"Native Hawaiian" = hd01_vd03,
"Samoan" = hd01_vd04,
"Tongan" = hd01_vd05,
"Other Polynesian" = hd01_vd06,
"Guamanian or Chamorro" = hd01_vd08,
"Marshallese" = hd01_vd09,
"Other Micronesian" = hd01_vd10,
"Fijian" = hd01_vd12,
"Other Melanesian" = hd01_vd13,
"Other Pacific Islander" = hd01_vd14,
"Two or more NHPI" = hd01_vd15
)

msa_nhpi_origin_pct<- msa_nhpi_origin_pct %>% rename(
"MSA"= geodisplaylabel,
"Total NHPI Alone" = hd01_vd01,
"Native Hawaiian" = pct_hd01_vd03,
"Samoan" = pct_hd01_vd04,
"Tongan" = pct_hd01_vd05,
"Other Polynesian" = pct_hd01_vd06,
"Guamanian or Chamorro" = pct_hd01_vd08,
"Marshallese" = pct_hd01_vd09,
"Other Micronesian" = pct_hd01_vd10,
"Fijian" = pct_hd01_vd12,
"Other Melanesian" = pct_hd01_vd13,
"Other Pacific Islander" = pct_hd01_vd14,
"Two or more NHPI" = pct_hd01_vd15)

msa_pop <- msa_pop %>% rename(
  MSA = geodisplaylabel,
  `Total Population`= est_tot_pop,
  `Asian Alone` = est_aa_alone,
  `Asian Alone % Total Pop` = pct_aa_alone,
  `Asian Combo` = est_aa_combo,
  `Asian Combo % Total Pop` = pct_aa_combo,
  `NHPI Alone` = est_nhpi_alone,
  `NHPI Alone % Total Pop` = pct_nhpi_alone,
  `NHPI Combo` = est_nhpi_combo,
  `NHPI Combo % Total pop` = pct_nhpi_combo
)

msa_rawnumbers <- c("MSA", "Total Population", "Asian Alone", "Asian Combo", "NHPI Alone", "NHPI Combo")
msa_percent <- c("MSA", "Total Population", "Asian Alone % Total Pop", "Asian Combo % Total Pop", "NHPI Alone % Total Pop", "NHPI Combo % Total pop")
msa_origin_percent <- c()

 msa_display_table <- function(data, which_estimates){
   data %>%
     select(which_estimates)%>%
     arrange(MSA)%>%
    select(MSA,starts_with("Total population"),everything()) %>%
      datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'Brt',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 1),
                lengthMenu = c(25, 50, 100), pageLength = 50))
 }


```



```{r setup pop, include = FALSE}


###Data highlight sentence
msa_largestAAprop <- msa_pop %>% top_n(1, `Asian Alone % Total Pop`) %>% pull(MSA)
msa_largestAAprop_number <- msa_pop %>% top_n(1, `Asian Alone % Total Pop`) %>% pull(`Asian Alone % Total Pop`)
msa_largestAAprop_number<- round(msa_largestAAprop_number*100,0)


```



<div class="jumbotron">
  <div class="container">
  <h1>Metro Area Data</h1>
  <p> About `r msa_largestAAprop_number`% of the population in `r msa_largestAAprop` is Asian American, the highest in the country.</p>
<div class="btn-group" role="group" aria-label="Basic example">
  <a href="metro_data.html#percent-aapi-population" type="button" class="btn btn-primary">AAPI Population</a>
  <a href="metro_data.html#asian-american-detailed-origin" type="button" class="btn btn-primary">Asian Detailed Origin</a>
  <a href="metro_data.html#nhpi-american-detailed-origin" type="button" class="btn btn-primary">NHPI Detailed Origin</a>
</div>
</div>
</div>

# Population {.tabset .tabset-fade .tabset-pills}
<a href="#top"><div style="text-align:center">Back to Top</a></div>

> Population data is complied using Tables: [B02001](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02001), [B02011](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02011), and [B02012](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02012) from the 2016 ACS 5-Year estimates.

  


## Percent AAPI Population 


```{r pop-pct, echo=FALSE, message=FALSE, warning=FALSE}

  
 msa_display_table(msa_pop,msa_percent) %>% 
  formatCurrency(columns = c(2),currency = "", interval = 3, mark = ",", digits=0) %>%
  formatPercentage(columns = c(3,4,5,6),digits = 2)


```


## AAPI Population


```{r pop-number, echo=FALSE, message=FALSE, warning=FALSE}

  
msa_display_table(msa_pop,msa_rawnumbers) %>% 
  formatCurrency(columns = c(2,3,4,5,6),currency = "", interval = 3, mark = ",", digits=0)


```


# Asian American Detailed Origin {.tabset .tabset-fade .tabset-pills}
<a href="#top"><div style="text-align:center">Back to Top</a></div>

> Population data is complied using Tables: [B02015](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02015) from the 2016 ACS 5-Year estimates.


## Percent Asian Detailed Origin

```{r pop-aa-origin-pct, echo=FALSE, message=FALSE, warning=FALSE}

  
msa_display_table(msa_aa_origin_pct, colnames(msa_aa_origin_pct)) %>% 
  formatCurrency(columns = c(2),currency = "", interval = 3, mark = ",", digits=0)%>%
  formatPercentage(columns = c(3:26), digits= 1)


```


## Asian Detailed Origin

```{r pop-aa-origin-number, echo=FALSE, message=FALSE, warning=FALSE}

  
msa_display_table(msa_aa_origin_counts, colnames(msa_aa_origin_counts)) %>% 
  formatCurrency(columns = c(2:26),currency = "", interval = 3, mark = ",", digits=0)


```

# NHPI American Detailed Origin {.tabset .tabset-fade .tabset-pills}
<a href="#top"><div style="text-align:center">Back to Top</a></div>

> Population data is complied using Tables: [B02016](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B02016) from the 2016 ACS 5-Year estimates.


## Percent NHPI Detailed Origin

```{r pop-NHPI-origin-pct, echo=FALSE, message=FALSE, warning=FALSE}

  
msa_display_table(msa_nhpi_origin_pct, colnames(msa_nhpi_origin_pct)) %>% 
  formatCurrency(columns = c(2),currency = "", interval = 3, mark = ",", digits=0)%>%
  formatPercentage(columns = c(3:13), digits= 1)


```


## NHPI Detailed Origin

```{r pop-NHPI-origin-number, echo=FALSE, message=FALSE, warning=FALSE}

  
msa_display_table(msa_nhpi_origin_counts, colnames(msa_nhpi_origin_counts)) %>% 
  formatCurrency(columns = c(2:13),currency = "", interval = 3, mark = ",", digits=0)


```