---
title: ''
output: html_document
---

```{r setup, include=FALSE}

## Loading Packages
library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)
library(acs)
library(stringr)

## Setting Formatting for output
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
## Formatting for Graphics
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)


#Read in files
state_edu<- readxl::read_xlsx("raw_data/state/state_edu.xlsx")
state_LEP<- readxl::read_xlsx("raw_data/state/state_LEP.xlsx")
state_nativity<- readxl::read_xlsx("raw_data/state/state_nativity.xlsx")
state_poverty<- readxl::read_xlsx("raw_data/state/state_poverty.xlsx")
state_pop<- readxl::read_xlsx("raw_data/state/state_pop.xlsx")
state_cvap<- readxl::read_xlsx("raw_data/state/state_cvap_alone.xlsx")
## [rename the variable to pop_id] state_edu <- state_edu %>% rename(pop_id = popgroupid)

## Using the lookup table to merge in Group Names and the proper population ID names
pop_id_lookup <- read_csv("raw_data/pop_id_lookup.csv") #Look-up table
state_edu<-state_edu %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
state_LEP<-state_LEP %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
state_nativity<-state_nativity %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
state_poverty<-state_poverty %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
state_pop<-state_pop %>% left_join(pop_id_lookup) %>% select(-geoid, -pop_id)
### Specifying Groups
groups_alone <- c("Total population", "Asian alone", "NHPI alone")
groups_combo <- c("Total population", "Asian alone or combo", "NHPI alone or combo")
groups_race <- c("Total population", "Asian alone", "NHPI alone", "Asian alone or combo", "NHPI alone or combo")

groups_asian_detail_alone <-pop_id_lookup %>%
  filter(group_id == "Asian Detail") %>% 
  select(group_name) %>% pull()

groups_asian_detail_combo <-pop_id_lookup %>%
  filter(group_id == "Asian Detail Combo") %>% 
  select(group_name) %>%  pull()

groups_nhpi_detail_alone <-pop_id_lookup %>%
  filter(group_id == "NHPI Detail") %>% 
  select(group_name) %>%  pull()

groups_nhpi_detail_combo <-pop_id_lookup %>%
  filter(group_id == "NHPI Detail Combo") %>% 
  select(group_name) %>%  pull()
  

## Function that will take excel file and make it long
state_convert_long <- function(data){
  data %>%
  gather(estimate_type,
         estimate,
         -State,
         -Group,
         -group_id)
}


 state_display_table <- function(data, whichgroup, whichestimates){
   data %>%
     filter(Group %in% whichgroup) %>%
     filter(estimate_type %in% whichestimates) %>%
     select(-group_id) %>%
     mutate(long_key=paste(Group, estimate_type, sep=": ")) %>% #Combining Pop_ID and Estimate type
     select(-Group, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) %>%
     select(State,starts_with("Total population"),everything()) %>% 
      datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 1),
                lengthMenu = c(25, 50, 100), pageLength = 50))
 }


```

```{r setup pop, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
state_pop <- state_pop %>% 
  mutate(est_tot_pop = 
            case_when( checking_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
         est_state_pop  =
          case_when( checking_state_pop == 1 ~  NA_real_ ,TRUE ~ est_state_pop))

# Dropping those indicators
state_pop <- state_pop %>% select(-checking_tot_pop,
                                  -checking_state_pop)



state_pop_map <- state_pop

# Renaming columns
state_pop<- state_pop %>% rename(Total = est_tot_pop,
         `Population` = est_state_pop,
         Group = group_name,
         `% of the Pop`= pct_pop,
         State = geodisplaylabel)



## Converting it to Long
state_pop_long <- state_convert_long(state_pop)
## add all outcome data here (just replace state_edu with another data name)


## Column Specification
pop_estimates <- c("Total")
pop_percent <- c("% of the Pop")




### Calculating Average for the sentence
avg_aa_pop <- state_pop %>% filter(Group == "Asian alone") %>% select(State, `% of the Pop`) %>%  summarize(mean = mean(`% of the Pop`, na.rm=TRUE)) %>% pull() %>% round(.,4)
avg_aa_pop <- avg_aa_pop*100
 
avg_pi_pop <- state_pop %>% filter(Group == "NHPI alone") %>% select(State, `% of the Pop`) %>%  summarize(mean = mean(`% of the Pop`, na.rm=TRUE)) %>% pull() %>% round(.,4)
avg_pi_pop <- avg_pi_pop*100

state_largest_aaprop <- state_pop %>% filter(Group == "Asian alone") %>% select(State, `% of the Pop`) %>%  top_n(1,`% of the Pop` )%>% pull(1) 
state_largest_aaprop_number <- state_pop %>% filter(Group == "Asian alone") %>% select(State, `% of the Pop`) %>%  top_n(1,`% of the Pop` )%>% pull(2)  %>% round(.,4) 
state_largest_aaprop_number<- state_largest_aaprop_number*100



```

```{r setup cvap-alone, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
state_cvap <- state_cvap %>% 
  mutate(est_state_cvap = 
            case_when( checking_state_cvap == 1 ~  NA_real_ ,TRUE ~ est_state_cvap),
            est_aapi_cvap = 
            case_when( checking_aapi_cvap == 1 ~  NA_real_ ,TRUE ~ est_aapi_cvap),
         est_aapi_pop  =
          case_when( checking_aapi_pop == 1 ~  NA_real_ ,TRUE ~ est_aapi_pop))

# Dropping those indicators
state_cvap <- state_cvap %>% select(-checking_state_cvap,
                                  -checking_aapi_pop,
                                  -checking_aapi_cvap)

# Create Columns
state_cvap <- state_cvap %>% mutate(
 pct_state_cvap   = est_state_cvap /est_state_pop)

state_cvap_map <- state_cvap

# Renaming columns
state_cvap<- state_cvap %>% rename(`Total Population`= est_state_pop,
         `Total CVAP` = est_state_cvap,
         `AAPI Pop`= est_aapi_pop,
         `AAPI CVAP`= est_aapi_cvap,
         `AAPI Share of CVAP` = pct_aapi_cvap,
         `AAPI Share of Pop`= pct_aapi_pop,
         `% State CVAP`= pct_state_cvap,
         State = geoname)


### Calculating Average for the sentence
avg_state_cvap <- state_cvap %>% select(State, `% State CVAP`) %>%  summarize(mean = mean(`% State CVAP`, na.rm=TRUE)) %>% pull() %>% round(.,4)
avg_state_cvap <- avg_state_cvap*100

avg_aapi_cvap <- state_cvap %>% select(State, `AAPI Share of CVAP`) %>%  summarize(mean = mean(`AAPI Share of CVAP`, na.rm=TRUE)) %>% pull() %>% round(.,4)
avg_aapi_cvap <- avg_aapi_cvap*100

```



```{r setup education, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
state_edu <- state_edu %>% 
  mutate(est_hsless = 
            case_when( check_hsless == 1 ~  NA_real_ ,TRUE ~ est_hsless),
         est_hsged  =
          case_when( check_hsged == 1 ~  NA_real_ ,TRUE ~ est_hsged),
         est_somecollegeaa  =
          case_when( check_somecollegeaa == 1 ~  NA_real_ ,TRUE ~ est_somecollegeaa),
         est_bahigher  =
          case_when( check_bahigher == 1 ~  NA_real_ ,TRUE ~ est_bahigher))
# Dropping those indicators
state_edu <- state_edu %>% select(-check_hsless,
                                  -check_hsged,
                                  -check_somecollegeaa,
                                  -check_bahigher)

# Create Columns
state_edu <- state_edu %>% mutate(
 pct_hsless   = est_hsless/est_totpop,
 pct_bahigher = est_bahigher/ est_totpop,
 pct_somecollegeaa = est_somecollegeaa / est_totpop,
 pct_hsged = est_hsged / est_totpop)


state_edu_map <- state_edu

# Renaming columns
state_edu<- state_edu %>% rename(`Total 25yrs+ old`= est_totpop,
         `Less than HS` = est_hsless,
         `HS or GED` = est_hsged,
         `Some College or AA` = est_somecollegeaa,
         `BA or higher` = est_bahigher,
         Group = group_name,
         `% Less than HS`= pct_hsless,
         `% HS and GED` = pct_hsged,
         `% Some College or AA` = pct_somecollegeaa,
         `% BA or higher` = pct_bahigher,
         State = geodisplaylabel)



## Converting it to Long
state_edu_long <- state_convert_long(state_edu)
## add all outcome data here (just replace state_edu with another data name)


## Column Specification
education_estimates <- c("Total 25yrs+ old", "Less than HS", "HS or GED", "Some College or AA", "BA or higher")
education_percent <- c("% Less than HS", "% BA or higher", "% HS and GED", "% Some College or AA")



### Calculating Average for the sentence
avg_hs_less <- state_edu %>% filter(Group == "Total population") %>% select(State, `% Less than HS`) %>%  summarize(mean = mean(`% Less than HS`)) %>% pull() %>% round(.,4)
avg_hs_less <- avg_hs_less*100
 
avg_ba_higher <- state_edu %>% filter(Group == "Total population") %>% select(State,  `% BA or higher`) %>%  summarize(mean = mean( `% BA or higher`)) %>% pull() %>% round(.,4)
avg_ba_higher <- avg_ba_higher*100


```

```{r setup LEP, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
state_LEP <- state_LEP %>% 
  mutate(est_tot_pop = 
            case_when( checking_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
    est_lep = 
            case_when( checking_lep == 1 ~  NA_real_ ,TRUE ~ est_lep),
         est_other_lang  =
          case_when( checking_other_lang == 1 ~  NA_real_ ,TRUE ~ est_other_lang))
        
# Dropping those indicators
state_LEP <- state_LEP %>% select(-checking_tot_pop,
                                  -checking_lep,
                                  -checking_other_lang)

# Create Columns
state_LEP <- state_LEP %>% mutate(
pct_lep   = est_lep/est_other_lang)


state_LEP_map <- state_LEP

# Renaming columns
state_LEP<- state_LEP %>% rename(Total = est_tot_pop,
         `LEP` = est_lep,
         Group = group_name,
         `Speak other language` = est_other_lang,
         `% LEP`= pct_lep,
         State = geodisplaylabel)


## Converting it to Long
state_LEP_long <- state_convert_long(state_LEP)
## add all outcome data here (just replace state_edu with another data name)

## Column Specification
LEP_estimates <- c("Total", "LEP", "Speak Other Language")
LEP_percent <- c("% LEP")


### Calculating Average for the sentence
avg_lep <- state_LEP %>% filter(Group == "Total population") %>% select(State, `% LEP`) %>%  summarize(mean = mean(`% LEP`,na.rm = T)) %>% pull() %>% round(.,4)
avg_lep <- avg_lep*100

```



```{r setup nativity, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
state_nativity <- state_nativity %>% 
  mutate(est_tot_pop = 
            case_when( checking_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
         est_foreign_born  =
          case_when( checking_foreign_born == 1 ~  NA_real_ ,TRUE ~ est_foreign_born))


# Dropping those indicators
state_nativity <- state_nativity %>% select(-checking_tot_pop,
                                  -checking_foreign_born)

# Create Columns
state_nativity <- state_nativity %>% mutate(
pct_foreign_born   = est_foreign_born / est_tot_pop)

state_nativity_map <- state_nativity

# Renaming columns
state_nativity<- state_nativity %>% rename(Total = est_tot_pop,
         `Foreign Born` = est_foreign_born,
         Group = group_name,
         `% Foreign Born`= pct_foreign_born,
         State = geodisplaylabel)



## Converting it to Long
state_nativity_long <- state_convert_long(state_nativity)
## add all outcome data here (just replace state_edu with another data name)


## Column Specification
nativity_estimates <- c("Total", "Foreign Born")
nativity_percent <- c("% Foreign Born")



### Calculating Average for the sentence
avg_foreign_born <- state_nativity %>% filter(Group == "Total population") %>% select(State, `% Foreign Born`) %>%  summarize(mean = mean(`% Foreign Born`, na.rm = T)) %>% pull() %>% round(.,4)
avg_foreign_born <- avg_foreign_born*100
 
```

```{r setup poverty, include = FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
state_poverty <- state_poverty %>% 
  mutate(est_tot_pop = 
            case_when( checking_tot_pop == 1 ~  NA_real_ ,TRUE ~ est_tot_pop),
         est_below_pov  =
          case_when( checking_below_pov == 1 ~  NA_real_ ,TRUE ~ est_below_pov),
         est_above_pov  =
          case_when( checking_above_pov == 1 ~  NA_real_ ,TRUE ~ est_above_pov))

# Dropping those indicators
state_poverty <- state_poverty %>% select(-checking_tot_pop,
                                  -checking_below_pov,
                                  -checking_above_pov)

# Create Columns
state_poverty <- state_poverty %>% mutate(
 pct_below_pov   = est_below_pov/est_tot_pop,
 pct_above_pov = est_above_pov/ est_tot_pop)


state_poverty_map <- state_poverty

# Renaming columns
state_poverty<- state_poverty %>% rename(Total = est_tot_pop,
         `Below Poverty` = est_below_pov,
         `Above Poverty` = est_above_pov,
         Group = group_name,
         `% Below Poverty`= pct_below_pov,
         `% Above Poverty` = pct_above_pov,
         State = geodisplaylabel)




## Converting it to Long
state_poverty_long <- state_convert_long(state_poverty)
## add all outcome data here (just replace state_poverty with another data name)


## Column Specification
poverty_estimates <- c("Total", "Below Poverty", "Above Poverty")
poverty_percent <- c("% Below Poverty", "% Above Poverty")



### Calculating Average for the sentence
avg_below_pov <- state_poverty %>% filter(Group == "Total population") %>% select(State, `% Below Poverty`) %>%  summarize(mean = mean(`% Below Poverty`, na.rm=T)) %>% pull() %>% round(.,4)
avg_below_pov <- avg_below_pov*100



```




<div class="jumbotron">
  <div class="container">
  <h1>State Data</h1>
  <p> About `r state_largest_aaprop_number`% of the population in `r state_largest_aaprop` is Asian American, the highest in the country.</p>
<div class="btn-group" role="group" aria-label="Basic example">
  <a href="state_data.html#citizen-voting-age-population" type="button" class="btn btn-primary">CVAP</a>
  <a href="state_data.html#education" type="button" class="btn btn-primary">Education</a>
  <a href="state_data.html#limited-english-proficiency" type="button" class="btn btn-primary">LEP</a>
  <a href="state_data.html#nativity" type="button" class="btn btn-primary">Nativity</a>
  <a href="state_data.html#poverty" type="button" class="btn btn-primary">Poverty</a>
</div>
</div>
</div>


# Resident Population {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> Detailed Origin data is complied using Table [B01003](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B01003) from the 2015 ACS 5-Year estimates.

Nationally, about **`r avg_aa_pop`**% of the population is Asian American, and **`r avg_pi_pop`**% of the population is NHPI.


## Visualize Data

```{r pop visualize, echo=FALSE, message=FALSE, warning=FALSE}


 state_pop_map <- state_pop_map %>%
  gather(estimate_type,
         estimate,
         -geodisplaylabel,
         -group_name,
         -group_id)

 state_pop_map <- state_pop_map %>%
     filter(group_name %in% groups_alone) %>%
   filter(str_detect(estimate_type, "est_tot")) %>%
     select(-group_id) %>%
     mutate(long_key=paste(group_name, estimate_type, sep="_")) %>% #Combining Pop_ID and Estimate type
     select(-group_name, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) 
  

state_pop_map <- state_pop_map %>% mutate(
  state_pop = `Total population_est_tot_pop`,
  state_pop_mill =`Total population_est_tot_pop`/1000000,
  asian_pop = `Asian alone_est_tot_pop`,
  nhpi_pop = `NHPI alone_est_tot_pop`)

x <- c("{point.name}:", "Asian Alone:","NHPI Alone:")
title<-"State Population"
y <- c(" {point.value:.2f} Million", " {point.asian_pop:,.0f}",
" {point.nhpi_pop:,.0f}")
#style <- "style=font-size:80%"

data(usgeojson)
highchart() %>%
  hc_title(text = "State Population", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_chart(backgroundColor = "transparent") %>%
  hc_add_series_map(usgeojson, state_pop_map, name = "State Population", value = "state_pop_mill", joinBy = c("name", "geodisplaylabel"),
                    borderColor= "transparent") %>%
  hc_tooltip(pointFormat = tooltip_table(x,y,title), useHTML=T,  headerFormat= "")%>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops = color_stops(5),labels= list(format = "{value}"),showInLegend=T) %>%
  hc_legend(title = list(text= "Statewide Population (millions)", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) %>% 
  #hc_legend(layout = "vertical", align = "right",
   #         floating = TRUE, valueDecimals = 0, valueSuffix = " thousand") 
  hc_exporting(enabled = TRUE)
```




## Major Racial Groups


```{r pop-race, echo=FALSE, message=FALSE, warning=FALSE}

  
 state_display_table(state_pop_long, groups_race, pop_estimates) %>% 
  formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0) 

```

## Asian Alone


```{r pop-asian-alone, echo=FALSE, message=FALSE, warning=FALSE}

  state_pop %>%
    filter(group_id %in% "Asian Detail") %>%
    select(-group_id, - `% of the Pop`,-`Population`) %>%
    spread(Group,Total,fill = NA) %>%
    datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% 
  formatCurrency(columns = c(2:22),currency = "", interval = 3, mark = ",", digits=0) 

```

## NHPI Alone


```{r pop-nhpi-alone, echo=FALSE, message=FALSE, warning=FALSE}

  
 state_display_table(state_pop_long, groups_nhpi_detail_alone, pop_estimates) %>% 
  formatCurrency(columns = c(2:10),currency = "", interval = 3, mark = ",", digits=0) 

```

## Asian Combo


```{r pop-asian-combo, echo=FALSE, message=FALSE, warning=FALSE}

  
  state_pop %>%
    filter(group_id %in% "Asian Detail Combo") %>%
    select(-group_id, - `% of the Pop`,-`Population`) %>%
    spread(Group,Total,fill = NA) %>%
    datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% 
  formatCurrency(columns = c(2:22),currency = "", interval = 3, mark = ",", digits=0)

```

## NHPI Combo


```{r pop-nhpi-combo, echo=FALSE, message=FALSE, warning=FALSE}

  
 state_display_table(state_pop_long, groups_nhpi_detail_combo, pop_estimates) %>% 
  formatCurrency(columns = c(2:10),currency = "", interval = 3, mark = ",", digits=0) 

```








# Education {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>


> Educational Attainment data is complied using Table [B15002](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B15002) from the 2015 ACS 5-Year estimates.

Nationally, about **`r avg_hs_less`**% of Americans have less than a High School diploma and about **`r avg_ba_higher`**% have a Bachelor's Degree or higher.

## Visualize Data

```{r edu visualize, echo=FALSE, message=FALSE, warning=FALSE}


 state_edu_map <- state_edu_map %>%
  gather(estimate_type,
         estimate,
         -geodisplaylabel,
         -group_name,
         -group_id)



 state_edu_map <- state_edu_map %>%
     filter(group_name %in% groups_alone) %>%
     filter(str_detect(estimate_type, "pct_")) %>%
     select(-group_id) %>%
     mutate(long_key=paste(group_name, estimate_type, sep="_")) %>% #Combining Pop_ID and Estimate type
     select(-group_name, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) 
  

state_edu_map <- state_edu_map %>% mutate(
  pct_state_bahigher = round(`Total population_pct_bahigher`*100,2),
  pct_asian_bahigher = round(`Asian alone_pct_bahigher`*100,2),
  pct_nhpi_bahigher = round(`NHPI alone_pct_bahigher`*100,2)
)

x <- c("{point.name}:", "Asian Alone:","NHPI Alone:")
title<-"Percent BA or Higher"
y <- c(" {point.value:.1f}%", " {point.pct_asian_bahigher:.1f}%",
" {point.pct_nhpi_bahigher:.1f}%")
#style <- "style=font-size:80%"

data(usgeojson)
highchart() %>%
  hc_title(text = "Bachelors Degree or Higher", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_chart(backgroundColor = "transparent") %>%
  hc_add_series_map(usgeojson, state_edu_map, name = "Education",value = "pct_state_bahigher", joinBy = c("name", "geodisplaylabel"),
                    borderColor= "transparent") %>%
  hc_tooltip(pointFormat = tooltip_table(x,y,title), useHTML=T,  headerFormat= "")%>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops = color_stops(5),labels= list(format = "{value}%"),showInLegend=T) %>%
  hc_legend(title = list(text= "Statewide Percentage", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) %>% 
  #hc_legend(layout = "vertical", align = "right",
   #         floating = TRUE, valueDecimals = 0, valueSuffix = "%") 
  hc_exporting(enabled = TRUE)

```


## % Asian & NHPI Alone


```{r EDU-alone-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_display_table(state_edu_long, groups_alone,education_percent) %>% formatPercentage(columns = c(2:13), digits = 2)

```

## % Asian & NHPI Combo


```{r EDU-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_display_table(state_edu_long, groups_combo,education_percent) %>% formatPercentage(columns = c(2:13), digits = 2)


```





# Limited English Proficiency {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> Limited English Proficiency (LEP) refers to the proportion of individuals who speak a language other than english at home & speak english less than "very well".
Limited English Proficiency data is complied using Table [B16004](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B16004) from the 2015 ACS 5-Year estimates.

Nationally Among Americans who speak a language other than english at home, about **`r avg_lep`**% of them speak English less than "very well".

## Visualize Data

```{r LEP visualize, echo=FALSE, message=FALSE, warning=FALSE}


 state_LEP_map <- state_LEP_map %>%
  gather(estimate_type,
         estimate,
         -geodisplaylabel,
         -group_name,
         -group_id)



 state_LEP_map <- state_LEP_map %>%
     filter(group_name %in% groups_alone) %>%
     filter(str_detect(estimate_type, "pct_")) %>%
     select(-group_id) %>%
     mutate(long_key=paste(group_name, estimate_type, sep="_")) %>% 
   #Combining Pop_ID and Estimate type
     select(-group_name, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) 
  
state_LEP_map <- state_LEP_map %>% mutate(
  pct_state_lep = round(`Total population_pct_lep`*100,2),
  pct_asian_lep = round(`Asian alone_pct_lep`*100,2),
  pct_nhpi_lep = round(`NHPI alone_pct_lep`*100,2)
)

x <- c("{point.name}:", "Asian Alone:","NHPI Alone:")
title<-"Percent of Limited English Proficiency"
y <- c(" {point.value:.1f}%", " {point.pct_asian_lep:.1f}%",
" {point.pct_nhpi_lep:.1f}%")
#style <- "style=font-size:80%"

data(usgeojson)
highchart() %>%
  hc_title(text = "Limited English Proficiency", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_chart(backgroundColor = "transparent") %>%
  hc_add_series_map(usgeojson, state_LEP_map, name = "Limited English Proficiency",value = "pct_state_lep", joinBy = c("name", "geodisplaylabel"),
                    borderColor= "transparent") %>%
  hc_tooltip(pointFormat = tooltip_table(x,y,title), useHTML=T,  headerFormat= "")%>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops = color_stops(5),labels= list(format = "{value}%"),showInLegend=T) %>%
  hc_legend(title = list(text= "Statewide Percentage", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) %>% 
  #hc_legend(layout = "vertical", align = "right",
   #         floating = TRUE, valueDecimals = 0, valueSuffix = "%") 
  hc_exporting(enabled = TRUE)

```


## % Asian & NHPI Alone

```{r LEP-alone-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_display_table(state_LEP_long, groups_alone,LEP_percent) %>% formatPercentage(columns = c(2:4), digits = 2)


```

## % Asian & NHPI Combo


```{r LEP-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_display_table(state_LEP_long, groups_combo,LEP_percent) %>% formatPercentage(columns = c(2:4), digits = 2)


```

## Raw Asian & NHPI Alone


```{r LEP-combo-Alone, echo=FALSE, message=FALSE, warning=FALSE}

  
 state_display_table(state_LEP_long, groups_alone,LEP_estimates) %>% 
  formatCurrency(columns = c(2:13),currency = "", interval = 3, mark = ",", digits=0) 


```


## Raw Asian & NHPI Combo

```{r LEP-Combo, echo=FALSE, message=FALSE, warning=FALSE}

 state_display_table(state_LEP_long, groups_combo,LEP_estimates) %>% 
  formatCurrency(columns = c(2:13),currency = "", interval = 3, mark = ",", digits=0) 



```




# Nativity {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> Nativity data is complied using Table [B05012](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B05012) from the 2015 ACS 5-Year estimates.

Nationally, about **`r avg_foreign_born`**% of Americans are foreign born.

## Visualize Data

```{r nativity visualize, echo=FALSE, message=FALSE, warning=FALSE}


 state_nativity_map <- state_nativity_map %>%
  gather(estimate_type,
         estimate,
         -geodisplaylabel,
         -group_name,
         -group_id)



 state_nativity_map <- state_nativity_map %>%
     filter(group_name %in% groups_alone) %>%
     filter(str_detect(estimate_type, "pct_")) %>%
     select(-group_id) %>%
     mutate(long_key=paste(group_name, estimate_type, sep="_")) %>% #Combining Pop_ID and Estimate type
     select(-group_name, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) 
  

state_nativity_map <- state_nativity_map %>% mutate(
  pct_state_foreign_born = round(`Total population_pct_foreign_born`*100,2),
  pct_asian_foreign_born = round(`Asian alone_pct_foreign_born`*100,2),
  pct_nhpi_foreign_born = round(`NHPI alone_pct_foreign_born`*100,2)
)

x <- c("{point.name}:", "Asian Alone:","NHPI Alone:")
title<-"Percent Foreign Born"
y <- c(" {point.value:.1f}%", " {point.pct_asian_foreign_born:.1f}%",
" {point.pct_nhpi_foreign_born:.1f}%")
#style <- "style=font-size:80%"

data(usgeojson)
highchart() %>%
  hc_title(text = "Foreign Born Population", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_chart(backgroundColor = "transparent") %>%
  hc_add_series_map(usgeojson, state_nativity_map, name = "Nativity",value = "pct_state_foreign_born", joinBy = c("name", "geodisplaylabel"),
                    borderColor= "transparent") %>%
  hc_tooltip(pointFormat = tooltip_table(x,y,title), useHTML=T,  headerFormat= "")%>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops = color_stops(5),labels= list(format = "{value}%"),showInLegend=T) %>%
  hc_legend(title = list(text= "Statewide Percentage", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) %>% 
  #hc_legend(layout = "vertical", align = "right",
   #         floating = TRUE, valueDecimals = 0, valueSuffix = "%") 
  hc_exporting(enabled = TRUE)

```



## % Asian & NHPI Alone


```{r nativity-alone-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_display_table(state_nativity_long, groups_alone,nativity_percent) %>% formatPercentage(columns = c(2:4), digits = 2)


```

## % Asian & NHPI Combo



```{r nativity-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_display_table(state_nativity_long, groups_combo,nativity_percent) %>% formatPercentage(columns = c(2:4), digits = 2)


```

## Raw Asian & NHPI Alone


```{r nativity-combo-Alone, echo=FALSE, message=FALSE, warning=FALSE}

  
 state_display_table(state_nativity_long, groups_alone,nativity_estimates) %>% 
  formatCurrency(columns = c(2:7),currency = "", interval = 3, mark = ",", digits=0) 


```


## Raw Asian & NHPI Combo

```{r nativity-Combo, echo=FALSE, message=FALSE, warning=FALSE}

 state_display_table(state_nativity_long, groups_combo,nativity_estimates) %>% 
  formatCurrency(columns = c(2:7),currency = "", interval = 3, mark = ",", digits=0) 



```


# Poverty {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> Poverty data is complied using Table [B17001](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B17001) from the 2015 ACS 5-Year estimates.

Nationally, about **`r avg_below_pov`**% of Americans are living below poverty line.

## Visualize Data

```{r poverty visualize, echo=FALSE, message=FALSE, warning=FALSE}


 state_poverty_map <- state_poverty_map %>%
  gather(estimate_type,
         estimate,
         -geodisplaylabel,
         -group_name,
         -group_id)



 state_poverty_map <- state_poverty_map %>%
     filter(group_name %in% groups_alone) %>%
     filter(str_detect(estimate_type, "pct_")) %>%
     select(-group_id) %>%
     mutate(long_key=paste(group_name, estimate_type, sep="_")) %>% #Combining Pop_ID and Estimate type
     select(-group_name, -estimate_type)  %>% 
     spread(long_key, estimate,fill = NA) 
  

state_poverty_map <- state_poverty_map %>% mutate(
  pct_state_below_pov = round(`Total population_pct_below_pov`*100,2),
  pct_asian_below_pov = round(`Asian alone_pct_below_pov`*100,2),
  pct_nhpi_below_pov = round(`NHPI alone_pct_below_pov`*100,2)
)

x <- c("{point.name}:", "Asian Alone:","NHPI Alone:")
title<-"Percent Below Poverty"
y <- c(" {point.value:.1f}%", " {point.pct_asian_below_pov:.1f}%",
" {point.pct_nhpi_below_pov:.1f}%")
#style <- "style=font-size:80%"

data(usgeojson)
highchart() %>%
  hc_title(text = "Poverty", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_chart(backgroundColor = "transparent") %>%
  hc_add_series_map(usgeojson, state_poverty_map, name = "Below Poverty",value = "pct_state_below_pov", joinBy = c("name", "geodisplaylabel"),
                    borderColor= "transparent") %>%
  hc_tooltip(pointFormat = tooltip_table(x,y,title), useHTML=T,  headerFormat= "")%>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops = color_stops(5),labels= list(format = "{value}%"),showInLegend=T) %>%
  hc_legend(title = list(text= "Statewide Percentage", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) %>% 
  #hc_legend(layout = "vertical", align = "right",
   #         floating = TRUE, valueDecimals = 0, valueSuffix = "%") 
  hc_exporting(enabled = TRUE)

```



## % Asian & NHPI Alone


```{r poverty-alone-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_display_table(state_poverty_long, groups_alone,poverty_percent) %>% formatPercentage(columns = c(2:7), digits = 2)

```

## % Asian & NHPI Combo


```{r poverty-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_display_table(state_poverty_long, groups_combo,poverty_percent) %>% formatPercentage(columns = c(2:7), digits = 2)


```

## Raw Asian & NHPI Alone


```{r poverty-combo-Alone, echo=FALSE, message=FALSE, warning=FALSE}

  
 state_display_table(state_poverty_long, groups_alone,poverty_estimates) %>% 
  formatCurrency(columns = c(2:10),currency = "", interval = 3, mark = ",", digits=0) 


```


## Raw Asian & NHPI Combo

```{r poverty-Combo, echo=FALSE, message=FALSE, warning=FALSE}

 state_display_table(state_poverty_long, groups_combo,poverty_estimates) %>% 
  formatCurrency(columns = c(2:10),currency = "", interval = 3, mark = ",", digits=0) 



```



# Citizen Voting Age Population {.tabset .tabset-fade .tabset-pills}
<a href="#top"><button class="btn btn-outline-primary center-block btn-small"> Back to Top</button></a>

> CVAP data is complied using Table [B05003](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B05003) from the 2015 ACS 5-Year estimates.

Nationally, about **`r avg_state_cvap`**% of Americans are eligible to vote, while the national average number for AAPI is **`r avg_aapi_cvap`**%

## Visualize Data

```{r CVAP visualize, echo=FALSE, message=FALSE, warning=FALSE}

state_cvap_map <- state_cvap_map %>% mutate(
  pct_state_cvap = round(pct_state_cvap*100,2),
  pct_aapi_cvap = round(pct_aapi_cvap*100,2))

  

x <- c("{point.name}:", "AAPI Alone:")
title<-"Percent of CVAP"
y <- c(" {point.value:.1f}%", " {point.pct_aapi_cvap:.1f}%")
#style <- "style=font-size:80%"

data(usgeojson)
highchart() %>%
  hc_title(text = "CVAP", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_chart(backgroundColor = "transparent") %>%
  hc_add_series_map(usgeojson, state_cvap_map, name = "CVAP",value = "pct_state_cvap", joinBy = c("name", "geoname"),
                    borderColor= "transparent") %>%
  hc_tooltip(pointFormat = tooltip_table(x,y,title), useHTML=T,  headerFormat= "")%>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops = color_stops(5),labels= list(format = "{value}%"),showInLegend=T) %>%
  hc_legend(title = list(text= "Statewide Percentage", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) %>% 
  #hc_legend(layout = "vertical", align = "right",
   #         floating = TRUE, valueDecimals = 0, valueSuffix = "%") 
  hc_exporting(enabled = TRUE)

```





## Raw Asian & NHPI Alone


```{r cvap-alone-raw, echo=FALSE, message=FALSE, warning=FALSE}

state_cvap_estimate <- state_cvap %>% select(State, `Total CVAP`, `AAPI CVAP`, `Total Population`, `AAPI Pop`) 

datatable(state_cvap_estimate, extensions = list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:5),currency = "", interval = 3, mark = ",", digits=0)
```

## % Asian & NHPI alone


```{r CVAP-combo-pct, echo=FALSE, message=FALSE, warning=FALSE}

state_cvap_pct <- state_cvap %>% select(State, `AAPI Share of CVAP`, `AAPI Share of Pop`) 

datatable(state_cvap_pct, extensions = list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatPercentage(columns = c(2:3), digits = 2)


```



